Twists of supersymmetric gauge theories

### 2020-01-07 paper.tex
Edited 6d (1,1) section

\begin{remark}
This theory is in general only $\ZZ/2\ZZ$-graded.  If the symplectic representation $U = T^*W$ is of cotangent type, then it is possible to promote to the $\ZZ$-graded generalized BF theory $T^*[-1]\mr{Map}(\CC^3, W/\gg)$ \chris{up to modifying by an even degree shift -- need to saythis more carefully}.
\end{remark}

@@

Let us write the BRST fields in $\mc N=(1,1)$ super Yang Mills on $\RR^6$ as $c$, the ghost, along with:
\begin{itemize}
 \item Bosons: a gauge field $A$, along with 4 scalars $\{\phi_i\}$.  These transform in the vector representation of the R-symmetry group $\Spin(4)_R$, i.e. the tensor product $W_+ \otimes W_-$ of the two fundamental representations of $\Sp(W_+) \times \Sp(W_-)$.  We'll write just $\phi$ for the scalars, viewed as a section of the trivial $W_+ \otimes W_-$-bundle on $\RR^6$.
 \item Fermions: spinor fields $\lambda^+ \otimes u^+$ and $\lambda^- \otimes u^-$ valued in $S_+ \otimes W_+$ and $S_- \otimes W_-$ respectively.
\end{itemize}

@@

We already considered the holomorphic twist in the previous section.  The remaining three classes are new: they all arise via appropriate dimensional reductions from twists of 7d $\mc N=1$ super Yang-Mills.

\begin{theorem} \label{6d_rk11_twist_thm}
The twist of 6d $\mc N=(1,1)$ super Yang-Mills theory by a rank $(1,1)$ supercharge with 4 invariant directions on the product of a Calabi-Yau surface $S$ and an oriented 2-manifold $\Sigma$ is equivalent to mixed BF theory on the product $S \times \Sigma_{\mr{dR}}$. This twist degenerates to a one-parameter family of topological twists of the form $\map(S \times \Sigma_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
\end{theorem}

\begin{theorem} \label{6d_rk22_twist_thm}
The twist by a rank $(2,2)$ supercharge of 6d $\mc N=(1,1)$ super Yang-Mills theory on the product of a Calabi-Yau curve $C$ with an oriented 4-manifold $M_4$ is equivalent to mixed Chern-Simons theory on $C \times (M_4)_{\mr{dR}}$.
\end{theorem}

>>>>

\begin{remark} \label{6d_BF_remark}
This theory is in general only $\ZZ/2\ZZ$-graded.  If the symplectic representation $U = T^*W$ is of cotangent type, then it is possible to promote to the $\ZZ$-graded generalized BF theory $T^*[-1]\mr{Map}(\CC^3, W/\gg)$ \chris{up to modifying by an even degree shift -- need to complete this and say it more carefully}.
\end{remark}

@@

There is a 6d gauge theory with $\mc N=(1,1)$ supersymmetry obtained by dimensionally reducing the maximal super Yang-Mills theory on $\RR^{10}$ down to $\RR^6$. This theory is alternatively obtained by considering the $\mc N=(1,0)$ theory above with representation $U = T^*\gg$: the $\mc N=(1,0)$ supersymmetry algebra action can be promoted to an $\mc N=(1,1)$ supersymmetry action.  Let us write the BRST fields in $\mc N=(1,1)$ super Yang Mills theory on $\RR^6$ as $c$, the ghost, along with:
\begin{itemize}
 \item Bosons: a gauge field $A$, along with 4 scalars $\{\phi_i\}$.  These transform in the vector representation of the R-symmetry group $\Spin(4)_R$, i.e. the tensor product $W_+ \otimes W_-$ of the two fundamental representations of $\Sp(W_+) \times \Sp(W_-)$.  We'll write just $\phi$ for the scalars, viewed as a section of the trivial $W_+ \otimes W_-$-bundle on $\RR^6$.
 \item Fermions: spinor fields $\lambda^+ \otimes u^+$ and $\lambda^- \otimes u^-$ valued in $S_+ \otimes W_+$ and $S_- \otimes W_-$ respectively.
\end{itemize}

We can write the supersymmetry action here explicitly. \chris{though it isn't necessary: remove it?}

@@

We already considered the holomorphic twist in the previous section: it admits the following description.

\begin{theorem} \label{6d_holo_twist_thm}
The holomorphic twist of 6d $\mc N=(1,1)$ super Yang-Mills theory is perturbatively equivalent to holomorphic BF theory on $\CC^3$ with target given by the adjoint quotient $\gg/\gg$, i.e. the theory with fields $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$.
\end{theorem}

\begin{proof}
Take the description of the holomorphically twisted theory from Theorem \ref{thm:6dholomorphictwist}, and let $U = T^*\gg$.  One identifies the resulting description as a $\ZZ$-graded theory with a cotangent theory as described in Remark \ref{6d_BF_remark}.
\end{proof}

The remaining three classes of twists are new: they all arise via appropriate dimensional reductions from twists of 7d $\mc N=1$ super Yang-Mills.

\begin{theorem} \label{6d_rk11_twist_thm}
The twist of 6d $\mc N=(1,1)$ super Yang-Mills theory by a rank $(1,1)$ supercharge with 4 invariant directions on the product of a Calabi-Yau surface $S$ and an oriented 2-manifold $\Sigma$ is perturbatively equivalent to mixed BF theory on the product $S \times \Sigma_{\mr{dR}}$. This twist degenerates to a one-parameter family of topological twists of the form $\map(S \times \Sigma_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
\end{theorem}

\begin{proof}
We obtain this description by starting with the 1-parameter family of twisted theories from Theorem \ref{7d_holo_twist_thm}, and dimensionally reducing along one of the Calabi-Yau directions.  That is, by applying Proposition \ref{CS_to_BF_diml_red_prop} to the family of twists in 7-dimensions.
\end{proof}

\begin{theorem} \label{6d_rk22_twist_thm}
The twist by a rank $(2,2)$ supercharge of 6d $\mc N=(1,1)$ super Yang-Mills theory on the product of a Calabi-Yau curve $C$ with an oriented 4-manifold $M_4$ is perturbatively equivalent to mixed Chern-Simons theory on $C \times (M_4)_{\mr{dR}}$.
\end{theorem}

\begin{proof}
We now start with the twisted theory from Theorem \ref{7d_rank2_twist_thm}, with 5 invariant directions, and we dimensionally reduce in an de Rham direction.  That is, we apply Proposition \ref{CS_diml_red_prop}.
\end{proof}
